Macro Impacts

### 2016-07-12 Macro Impacts Revised.tex
Melt Zone stuff
Added the preliminaries of computing the partition of the energy of a
projectile impact into kinetic, elastic, and plastic energy terms of
the target.

>>>>

\section{Melt Zone}
As derived in "A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.

The connection between the energy of the projectile and the value $\alpha*R$ is given in the paper posted "Hypervelocity penetration modeling- momentum vs. energy and energy transfer mechanisms". A derivation is given for the decomposition of the energy of a projectile into kinetic, elastic and plastic terms in, for example, equations 32, 33, and 38.

Note that the results in the section "Penetration" in this paper "Hypervelocity penetration..." are for eroding rods -- but macro doesn't erode.  If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e. earth or moon), we'd set u = v, and s = 0 to eliminate the "eroding" effect.
